Data-driven Reduction of Multiscale Stochastic Dynamical Systems

### 2014-07-10 reducible_SDE/paper/paper_outline.tex
added more stuff for reducible sde paper

\item Doing slow variable reduction from SDEs using the Mahalanobis graph (using NIV for slow variable extraction)

\item We give a full mathematical analysis of the slow variable reduction/procedure, including necessary conditions and user configuration

>>>>

\item Extracting or reducing an SDE system to its slow variables using the Mahalanobis graph and NIVs

\item Full mathematical analysis of the slow variable reduction procedure, including necessary conditions for accurate recovery of the slow variables and a framework for empirically setting the algorithm parameters
